% Manuscript: submission to Cognitive Science
% jefan@stanford.edu, yamins@mit.edu, nicholas.turk-browne@yale.edu

\documentclass[11pt,letterpaper]{article}

% \usepackage{cogsci}
\usepackage{pslatex}
\usepackage{apacite}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage[all]{nowidow}
\usepackage[font=small,skip=0pt]{caption}
\usepackage{mathtools}
\usepackage{float}
\usepackage{courier}
\usepackage{placeins}
\usepackage{sidecap}
\usepackage{lineno}
\usepackage{authblk}
\usepackage{caption,setspace}

\usepackage{color}
\definecolor{Blue}{RGB}{50,50,200}
\newcommand{\revised}[1]{\textcolor{Blue}{#1}}

\captionsetup{font={normal,stretch=1.1}}
\setlength{\parindent}{2em}
\setlength{\parskip}{0.5em}
\renewcommand{\baselinestretch}{1.5}
\usepackage[letterpaper, margin=0.9in]{geometry}

% \setlength{\intextsep}{9pt}
\setlength{\belowcaptionskip}{-\baselineskip}\addtolength{\belowcaptionskip}{1.6ex}

\title{Consequences of visual production training for neural object representations}
\date{}

\author[1,3]{Judith E. Fan}
\author[2]{Jeffrey Wammes}
\author[3]{Jordan B. Gunn}
\author[3]{Rachel S. Lee}
\author[1]{Daniel L. K. Yamins}
\author[3]{Kenneth A. Norman}
\author[2]{Nicholas B. Turk-Browne}

\affil[1]{Department of Psychology, Stanford University, Stanford, CA 94305}
\affil[2]{Department of Psychology, Yale University, New Haven, CT 06520}
\affil[3]{Department of Psychology, Princeton University, Princeton, NJ 08544}

\renewcommand\Authands{ and }

\begin{document}
\maketitle

\begin{abstract}
\hyphenpenalty=1000 {Abstract goes here.}


\end{abstract}
\textbf{Keywords:}
communication; drawing; learning; perception and action; objects

\newpage
\linenumbers

\section*{Introduction}

\section*{Methods}

\section*{Results}

\section*{Discussion}

\section*{Code availability} The code for the analyses presented in this article will be made publicly available in a Github repository upon acceptance of this manuscript.

\section*{Data availability} The data presented in this article will be made publicly available in a figshare repository upon acceptance of this manuscript.

\section*{Acknowledgements}

This work was supported by NSF GRFP DGE-0646086, NIH R01 EY021755, R01 MH069456, and the David A. Gardner '69 Magic Project at Princeton University. Thanks to the Computational Memory and Turk-Browne labs for helpful comments.

\section*{Author contributions statement}

J.E.F., D.L.K.Y., N.B.T.-B., K.A.N. designed the study. J.E.F. performed the experiments. J.E.F., J.D.W., J.B.G., R.S.L. conducted analyses. J.E.F., J.D.W., J.B.G., R.S.L., K.A.N., and N.B.T.-B. planned analyses, interpreted results, and wrote the paper.

\section*{Additional information}

The authors declare no competing interests.

\bibliographystyle{apacite}

\setlength{\bibleftmargin}{.125in}
\setlength{\bibindent}{-\bibleftmargin}

\newpage
\bibliography{references}

\end{document}
