---
title: "Modeling variation across object assignment conditions in neurosketch study"
output: html_notebook
---

# Import some libraries 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidyboot)
library(ggthemes)
library(lme4)
library(stringr)
library(langcog)
library(jsonlite)
```

```{r}
proj_dir <- '/Users/judithfan/neurosketch'
csv_dir <- file.path(proj_dir,'csv')
diff <- read_csv(file.path(csv_dir,'neural_changes_by_surfroi_and_subject.csv'))
draw <- read_csv(file.path(csv_dir,'logistic_timeseries_drawing_neural_4way_logged.csv'))
```
```{r}


```



Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

